\name: A hierarchical Bayesian model for Supernova Cosmology

### 2018-02-26 papers/methods/paper.tex
Fixing typo

As such, staggering effort is being put into developing more sophisticated supernovae analyses. First used in ESSENSE analyses \citep{Wood-Vasey2007}, and then refined and improved in \citet{Kessler2009}, the role of simulations has become increasingly important in determining biases and validating models. \citet{Betoule2014} make use of redshift dependent $\mu$-bias to correct their analyses, and more recently \citet{Scolnic2016} and \citet{Kessler2017} explore simulation corrections as a function of redshift, stretch and colour to better remove fitting biases. Approximate Bayesian computation methods also make use of simulations, trading traditional likelihoods and analytic approximations for more robust models with the cost of increased computational time \citep{Weyant2013, Jennings2016}. Hierarchical Bayesian Models abound \citep{Mandel2009, March2011, March2014, Rubin2015, Shariff2016, Roberts2017}, however often face difficulties finding sufficient analytic approximations for complicated effects such as Malmquist bias.

>>>>

As such, staggering effort is being put into developing more sophisticated supernovae analyses. First used in ESSENSE analyses \citep{Wood-Vasey2007}, and then refined and improved in \citet{Kessler2009}, the role of simulations has become increasingly important in determining biases and validating models. \citet{Betoule2014} make use of redshift dependent $\mu$-bias to correct their analyses, and more recently \citet{Scolnic2016} and \citet{Kessler2017} explore simulation corrections as a function of redshift, stretch and colour to better remove fitting biases. Approximate Bayesian computation methods also make use of simulations, trading traditional likelihoods and analytic approximations for more robust models with the cost of increased computational time \citep{Weyant2013, Jennings2016}. Hierarchical Bayesian models abound \citep{Mandel2009, March2011, March2014, Rubin2015, Shariff2016, Roberts2017}, however often face difficulties finding sufficient analytic approximations for complicated effects such as Malmquist bias.
